\documentclass[10pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage[none]{hyphenat}
\usepackage[left=0.7in,top=0.2in,right=0.7in,bottom=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}

% Configure section titles
\titleformat{\section}{\large\bfseries\raggedright}{}{0em}{}[\rule{\textwidth}{1pt}]
\titlespacing{\section}{0pt}{1.5ex plus .1ex minus .2ex}{0ex plus .2ex}

% Custom command for header text
\newcommand{\headerline}[1]{\parbox[t]{\textwidth}{\raggedright #1}\vspace{0pt}}

\pagestyle{empty} % Remove page numbers

\begin{document}

%----------------------------------------------------------------------------------------
%	HEADER
%----------------------------------------------------------------------------------------
\begin{center}
    {\Huge \bf Ponza Matteo}\\
    \headerline{01/09/1997 | Valdagno (VI), Italy, 36078}
    \headerline{matteoponza@gmail.com | \href{https://www.linkedin.com/in/matteo-ponza-557136135/}{linkedin} | \href{https://github.com/PonzaMatteo}{github.com/PonzaMatteo}}
\end{center}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------
\section*{Professional Summary}
\noindent Practitioner of Extreme Programming methodologies including TDD, iterative and incremental design and development, pair programming, collective ownership, and simple design. Committed to technical excellence that enables business agility. 

\noindent A quote that I particularly like: \textit{``Software design is an exercise in human relationships''} - Kent Beck.

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE
%----------------------------------------------------------------------------------------
\section*{Professional Experience}

\noindent\textbf{StashAway - Staff Software Engineer (Part-Time)} \hfill \textit{Italy | Jan. 2025 - Present}\\
\noindent\textit{Software Engineer (Part-Time)} \hfill \textit{Italy | Sep. 2023 - Jan. 2025}\\
\noindent\textit{Software Engineer (Full-Time)} \hfill \textit{Singapore | Sep. 2019 - Sep. 2023}
\begin{itemize}[leftmargin=*, noitemsep, topsep=1pt]
    \item Design, develop and maintain mission-critical trading platform in a fault-tolerant and distributed system.
    \item Drive technical excellence and team growth through mentoring engineers, conducting code reviews, and leading strategic refactoring initiatives that improved system agility and reduced operational costs.
\end{itemize}

\begin{itemize}[leftmargin=*, noitemsep, topsep=1pt]
    \item Developed automations for supporting trading and anti-money laundering (AML) workflows.
    \item Executed large scale system migration and legacy system modernization projects.
\end{itemize}

\noindent\textbf{Trento University} - \textbf{Software Developer Internship} \hfill \textit{Italy | Apr. 2018 - Sep. 2018}
\begin{itemize}[leftmargin=*, noitemsep, topsep=1pt]
    \item Extended R package for circular statistics (circular).
    \item Implemented computational routines in R and C for statistical hypothesis testing, contributing to the CircStats package on R-Forge.
\end{itemize}

\noindent\textbf{GoSwift} - \textbf{Web Developer Intern} \hfill \textit{Estonia | Jun. 2016}
\begin{itemize}[leftmargin=*, noitemsep, topsep=1pt]
    \item Internship experience using Spring Framework and Angular JS.
\end{itemize}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section*{Education}

\noindent\textbf{Master's Degree in Software Engineering} \hfill \textit{Jul. 2023 - Oct. 2025}
\\ Free University of Bozen-Bolzano. Final Grade: 110 cum laude/110.
\\ Thesis: \textit{An Evaluation of Vector Database Systems for RAG Application.}
\\

\noindent\textbf{Bachelor's Degree in Computer Science} \hfill \textit{2016 - Jul. 2019}
\\ University of Trento. Final Grade: 110 cum laude/110.

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\section*{Technical Skills}
\begin{itemize}[leftmargin=*, noitemsep, topsep=1pt, parsep=0pt]
    \item \textbf{Programming Languages:} Kotlin, Go.
    \item \textbf{Technologies \& Tools:} Kafka, PostgreSQL, Temporal, GIT.
\end{itemize}

\end{document}