%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref}

\usepackage[left=0.50in,top=-0.2in,right=0.50in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\begin{document}
\begin{center}
    {\huge \bf Ponza Matteo}\\
    ---\\
    01/09/1997 | Valdagno (VI), Italy, 36078\\
    +39 3403675864 | matteoponza@gmail.com | \href{https://ponzamatteo.github.io/}{ponzamatteo.github.io}
\end{center}
\begin{rSection}{Education}
{\bf Banchelor Degree in Computer Science}
\hfill {\em September 2016 - Present} 
\\ Department of information engineering and computer science
\\ Università degli studi di Trento, Trento (Italy)

{\bf Erasmus Study in Estonia}
\hfill{\em January 2019- June 2019} 
\\ Tallinn University of Technology, Tallinn (Estonia)\\
\end{rSection}
\begin{rSection}{Work Experience}

    {\bf Junior Software developer}
    \hfill {\em 15/04/2018–01/09/2018}\\
    Curricular Internship at Università degli Studi di Trento. Development of a R package for circular statistics (r\href{https://r-forge.r-project.org/projects/circular/}{circular}). I've implemented mathematical routines in R and C languages.
    
    {\bf Website Developer}
    \hfill{\em 01/01/2016–01/01/2017} \\
    Creation of various websites using Wordpress: - Scientific conferences organized in my hometown(\href{http://laviadellescienze.altervista.org/}{link});\\
    - Camping for children: (\href{http://campomaglio.altervista.org/}{link}).\\
    {\bf Internship as Web Developer}
    \hfill {\em 01/06/2015–22/06/2015}\\
    GoSwift, Tallinn (Estonia)\\
    Internship experience in the context of project Erasmus+ Forins. Web Developer using the technologies: Spring and Angular JS.
\end{rSection}

\begin{rSection}{Language}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        Mother Tongue\ & Italian \\
        English & Level B2, Exam at Università degli studi di Trento \\
        \end{tabular}
\end{rSection}

\begin{rSection}{Technical skills}
    \begin{itemize}
        
        \item Experience with following programming languages gained during scholastic experiences and personal interest: Java, C/C++, Python, Javascript (Node.js), R and PHP.
        \item Experience on Machine Learning using Matlab and Python .
        \item Experience in website development using the Wordpress, HTML5 and CSS3.
        \item Knowledge of GIT as software version control.
    \end{itemize}    
\end{rSection}

\begin{rSection}{Soft Skills}
        {\bf Communication skills}\\
        In my experience as entertainer in a summer center for children I improved my communication and relational skills in order to organize educational activities with other entertainers and for carry out those activities with children.
        During my Erasmus experiences I improved my communication skills in a multicultural environment. \\
        {\bf Organizational Skills}\\
        Inclination to work and coordinate small working group improved during my experience as school and entertainer experience.
        Capability to supervise and organize the activities in a relatively critical environment strengthened with my experience as sport climbing instructor.
\end{rSection}

\begin{rSection}{Other Interest}
    {\bf Sport Climbing Instructor}
    \hfill {\em 01/10/2017–01/12/2018}\\
    ASD I Sogati, Valdagno (Italy) \\
    Sport climbing instructor recognized by Italian Federation for Sport Climbing (FASI). I have collaborated to organize and carry out sport climbing courses for children and adults.
\end{rSection}

\end{document}
