\documentclass[a4paper]{letter}

\RequirePackage{color,graphicx}
\usepackage[none]{hyphenat} 
\usepackage[big]{layaureo} 
% links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

% fonts
% \usepackage{fontspec} %for loading fonts
% \setmainfont{Neuton}

\signature{Matteo Ponza}
\address{Matteo Ponza\\
    Valdagno (VI), 36078, Italy\\
    (+39) 3403675864\\
    \href{mailto:matteoponza@gmail.com}{matteoponza@gmail.com}
    }
\begin{document}

\begin{letter}{
    Joy M \\
    HR Manager\\
    Lithan Academy Pte. Ltd\\
    11 Eunos Road 8 \#07-02 \\
    Lifelong Learning Institute\\
    Singapore 408601}

\opening{Dear Joy M,}
I am a student at the University of Trento, (Italy) and I am attaining a bachelor degree in computer science in July 2019. I am writing to you because I am interested in the position ``Software Developer'' that I have found on the following \href{https://www.linkedin.com/jobs/view/1341905034/}{LinkedIn page}.

I would love to join Lithan and help to improve the products and services it provides and consequently improve how the users of those products learn. In my experience as sport climbing instructor, I learned that there is always room for improvement in everything we do. So I am sure that working in a company that makes `learning' and `growing' pillars of his culture would be really motivating to give back the best to the company. 

As a student, I consider myself passionate and hard-working. Throughout my study career, I have been particularly interested in programming and mathematics courses. These courses allowed me to develop and improve my critical thinking and problem-solving skills. Furthermore, my curricular internship experience of implementing R and C programs for solving statistic problems honed my capability to handle complex problems systematically. I am sure that these abilities will be helpful at Lithan.

During my studies, I took part in two mobility programs, improving my adaptability to different cultures, environment and situations. So I am highly motivated to share and gain more experiences and take on new challenges.

About the technical requirements of the position, I can confirm that I have experience using web technologies such as HTML5, CSS3 and Javascript.

Attached is my resume. I look forward to hearing from you soon.
Should you require any additional information, please email me.
Thank you for your time and consideration.
\closing{Sincerely,}
\end{letter}
\end{document}