\documentclass[a4paper]{letter}

\RequirePackage{color,graphicx}
\usepackage[none]{hyphenat} 

% links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

% fonts
% \usepackage{fontspec} %for loading fonts
% \setmainfont{Neuton}

\signature{Matteo Ponza}
\address{Matteo Ponza\\
    Valdagno (VI), 36078, Italy\\
    (+39) 3403675864\\
    \href{mailto:matteoponza@gmail.com}{matteoponza@gmail.com}
    }
\begin{document}

\begin{letter}{
    Xia Jie Jessie \\
    Managing Director\\
    ThoughtWorks Pte. Ltd.\\
    18 Cross Street \#11-08\\
    China Square Central\\
    Singapore 048423}

\opening{Dear Xia Jie Jessie,}
I am a student at University of Trento, (Italy) and I am graduating with bachelor degree in computer science in July 2019. I am writing to you because I am interested in the position ``Graduate Software Developer'' that I have found in the company website.

Reading the mission of the company I have been impressed by the focus on the social impact that It has. I would love to dedicate myself to such a high aim during my work as I did in my volunteer experience as climbing instructor and as educational facilitator.

As a student, I consider myself passionate and hard-working. Throughout my study career, I have been particularly interested in programming and mathematics courses. These courses allowed me to develop and improve my critical thinking and problem-solving skills. Furthermore, my curricular internship experience of implementing R and C programs for solving statistic problems honed my capability to handle complex problems systematically. I am sure that these abilities will be helpful to a working team at ThoughtWorks while cooperating to solve difficult problems it will face.

During my studies, I took part in two mobility programs, improving my adaptability to different cultures, environment and situations. Stepping out my comfort zone has been really valuable for my personal and professional growth. So I am highly motivated to share and gain more experiences and take on new challenges.

Attached is my resume. I look forward to hearing from you soon.
Should you require any additional information, please email me.
Thank you for your time and consideration.
\closing{Sincerely,}
\end{letter}
\end{document}